Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-12 sections/correlated-sicm-and-fm.tex
Moved section about z-stacks to bottom of section. Not yet integrated
reworked up to indication
Questions:
- Is Nashimoto2015 really confocal?
- What is meant by "equalized photobleaching"

Yet,
a combination of SICM and $z$-stacking confocal FM yields more correlating
data than combinations of SICM and wide-field techniques as $z$-stacking
microscopy records data points in multiple $z$ planes. After imaging, these can
be aligned with the SICM data and non-correlating data can be separated from
correlating data. Still, there is a potential mismatch in resolution and the
data has to be processed after imaging to yield correlation. Yet, this
implementation is suitable for all, not only flat, fixed samples.

@@

% Bis hier...

@@

% Bis hier überarbeitet.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
  \caption{%
    \textbf{Combining SICM and SCM.}
    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
    VLPs adsorbed to the surface of COS 7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
    	\textit{Left:} Cell surface topography. 
    	\textit{Middle:} Fluorescence recording of the cell shown left. 
    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
    Reprinted with permission from ref \cite{Shevchuk2008}.
    \textbf{d:} Live COS 7 cells sequentially scanned by SSCM. Overlays of simmultaneously obtained 
    topographic and fluorescence scans. Fluorescence imaging was started 2 h 17 min after the first 
    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2 h 40 min. 
    Reprinted with permission from ref \cite{Gorelik2002}.
  }
  \label{fig:sicm+scm}
\end{figure}

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation, schematically illustrated in
figure \ref{fig:sicm+scm}a, allows not only for correlating studies in fixed samples (figure 
\ref{fig:sicm+scm}c), but also studies of dynamics in live samples (figure \ref{fig:sicm+scm}d).

>>>>

@@

% ich würde hier etwas zu potentiellen z-stacks + SICM sagen wollen, das hat
% ja meines Wissens nach noch niemand gemacht...
The applications reviewed above used only a single confocal layer. Yet,
a combination of SICM and $z$-stacking confocal FM could be used to yield more
correlating data. After imaging the entire volume that is scanned by SICM, the
data could be aligned and non-correlating data could be separated from
correlating data. If stage scanning would be omitted, the two measurements
could be performed simultaneously, but not synchronously.

@@

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
  \caption{%
    \textbf{Combining SICM and SCM.}
    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002}.
    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
    	\textit{Left:} Cell surface topography. 
    	\textit{Center:} Fluorescence recording of the cell shown left. 
    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
    Reprinted with permission from ref \cite{Shevchuk2008}.
    \textbf{d:} Live Cos-7 cells sequentially scanned by SSCM. Overlays of simultaneously obtained 
    topographic and fluorescence scans. Fluorescence imaging was started 2\,h 17\,min after the first 
    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2\,h 40\,min. 
    Reprinted with permission from ref \cite{Gorelik2002}.
  }
  \label{fig:sicm+scm}
\end{figure}

As the SICM and SCM data sets are recorded simultaneously, all data points inherently have a
correlating data point in the other set. This immediate correlation, schematically illustrated in
Fig.~\ref{fig:sicm+scm}a, allows not only for correlating studies in fixed
samples (Fig.~\ref{fig:sicm+scm}c), but also studies of dynamics in live
samples (Fig.~\ref{fig:sicm+scm}d).

% Bis hier
